Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
abstract

The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the SBE domain, either from the vocabularies themselves or from domain and data experts. All in all, this lead to TODO constraints on TODO vocabularies. We let the experts classify the constraints according to the severity if they are violated. Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain and range), over types that are simply stated using common constraint languages (e.g., cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible (e.g., constraints on network topologies).\ke{Thomas: Ok so?}

As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment and evaluated the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.

@@

In this paper, we discuss constraints on RDF data in general. Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data. We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.

>>>>

The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts. All in all, this lead to TODO constraints on TODO vocabularies\tb{246 constraints on six vocabularies}. We let the experts classify the constraints according to the severity if they are violated. Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain and range)\tb{and cardinality restrictions}, over types that are simply stated using common constraint languages (e.g., cardinality restrictions\tb{nein, nimm hier language tag cardinalities / cardinalty restrictions können formal in vokabularen spezifiert werden}) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible (e.g., constraints on network topologies\tb{vielleicht besser: constraint on graph-based structures}).

As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment and evaluated the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.

@@

In this paper, we discuss constraints on RDF data in general. Note that the data represented in RDF can be data in the sense of \emph{SBE} sciences, but also metadata about published or unpublished data. We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
